---
title: "Simulation Experiment: Standard normals"
author: "VM"
date: Feb 2016
output: 
  html_document: 
    keep_md: yes
---


###Simulation experiment with roll of dies.
###Experiment to prove mean will be concentrated around the popolution mean as the number of experiment increase and resembles bell curve
##For more details 

Shiny is an R pakage 


```{r}
library(UsingR); data(galton); library(ggplot2); 
nosim <- 1000
dat <- data.frame(
x = c(sample(1 : 6, nosim, replace = TRUE),
  apply(matrix(sample(1 : 6, nosim * 2, replace = TRUE), nosim), 1, mean),
  apply(matrix(sample(1 : 6, nosim * 3, replace = TRUE), nosim), 1, mean),
  apply(matrix(sample(1 : 6, nosim * 4, replace = TRUE), nosim), 1, mean)),
size = factor(rep(1 : 4, rep(nosim, 4))))

```

Plot to show the Mean for different dice rolls
========================================================

```{r, echo=FALSE}
    # plot histograms of means by sample size
    g <- ggplot(dat, aes(x = x, fill = size)) + geom_histogram(alpha = .20, binwidth=.25, colour = "black")
    g + facet_grid(.~ size)
    
```

Steps to use the application : How to simulate
========================================================
*step 1: Use slider to increase the number dice roll*  
*Step 2: Watch the histogram increase it density around mean*  
*Step 3: and it is evident that mean is same as popoluation mean as sampling size increases*
      
Conclusion
========================================================
This simulation demostrates that the more data that goes into the sample mean, 
the more concentrated its density/mass functions are around the population mean and
the histogram is also centered at 3.5. so it is 3 and 4 and concentrated aroung 3.5 as the simulation increses and resmebled bell curve)

